Report on a Safety Checker for Petri nets

### 2013-11-25 paper/workspace/main.tex
Updated report
Draft

>>>>

We constructed the following two invariants by applying the method Invariant Minimization.

\begin{itemize}
\item \verb?firewall__no_pred_called_with_zero__depth_2__fixed?: \verb?(assert (<= l3849 0))?
\item \verb?firewall__no_pred_called_with_zero__depth_1__fixed?: \verb?(assert (<= l739 0))?
\end{itemize}

\iic\ constructs the following two invariants.

\begin{itemize}
\item \verb=firewall__no_pred_called_with_zero__depth_1__fixed.spec=: \verb=(l739 < 1)=
\item \verb=firewall__no_pred_called_with_zero__depth_2__fixed.spec=: \verb=(l3849 < 1)=
\end{itemize}
